---
title: "Kmeans"
output: html_document
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(caret, data.table, ggplot2, ranger, magrittr, dplyr, BBmisc, ncdf)#ncdf is unsolved
```

## load the data for a few seconds


```{r}
columns <- read.table(
    "./data/kddcup.names",
    sep=":",
    skip=1,  # the first column name are the labels, but those are at the end!
    as.is=T
)
column_names <- c(columns[,1], 'label')

connection_events <- read.csv(
    "./data/kddcup.data_10_percent.gz",
    col.names=column_names
)

setDT(connection_events)  # convert from data.frame to data.table
```

## select the data from connection_events

Try to use kmeans
1. learn how to select columns except the label

This code is changing discrete strings into number
```{r}
connection_events$protocol_type <- as.integer(factor(connection_events$protocol_type))
connection_events$service <- as.integer(factor(connection_events$service))
connection_events$flag <- as.integer(factor(connection_events$flag))
kmeansdata <- connection_events[,1:41]
```

## it should be 5 catogries and forget normalization **Try kmeans 4 classifications


```{r kmeans, echo=FALSE}
set.seed(20)
kmeansdata <- normalize(kmeansdata, method = "standardize", range = c(0, 1), margin = 1L, on.constant = "quiet")
irisCluster <- kmeans(kmeansdata, 5, nstart = 20)

```

irisCluster returns cluster, centers, totss and so on.

## add new feature: is_kmeans_1, is_kmeans_2, is_kmeans_3, is_kmeans_4

```{r}

col.name = "a"
df <- data.frame(placeholder_name =  as.integer(irisCluster$`cluster`==i))
names(df)[names(df) == "placeholder_name"] <- col.name
assign(col.name, "col1")
assign(paste(col.name), 1:4)

df <- data.frame(mget(col.name))

```


## Variable as a column name in data frame 

```{r}
for(i in 1:5){
  variablename = paste("is_kmeans", i, sep = "_")
  
  subname = paste("connection_events$is_kmeans", i, sep = "_")
  print(subname)
  assign(subname, as.integer(irisCluster$`cluster`==i))
}
for(i in 1:5){
  subname = paste("connection_events$is_kmeans", i, sep = "_")
  eval(parse(text=paste0(subname, ' <- as.integer(irisCluster$`cluster`==1)')))
}
for(i in 1:5){
  name = paste0("is_kmeans",i+10)
  connection_events[[name]]<- as.integer(irisCluster$`cluster`==i)
}

connection_events
connection_events$is_kmeans_1 <- as.integer(irisCluster$`cluster`==1)
connection_events$is_kmeans_2 <- as.integer(irisCluster$`cluster`==2)
connection_events$is_kmeans_3 <- as.integer(irisCluster$`cluster`==3)
connection_events$is_kmeans_4 <- as.integer(irisCluster$`cluster`==4)
connection_events$is_kmeans_5 <- as.integer(irisCluster$`cluster`==5)
connection_events<-connection_events[,c(1:47)]
connection_events
```
## Try to change the order for the columns which is not prefect order for me as is_kmeans_4 is 43th.
This function below could reorder any column to the first column!
Here is how it works:

```{r}
new_df <- connection_events %>% select(label, everything())
new_df
```
It solves my problems!
Thanks to https://stackoverflow.com/questions/22286419/move-column-to-first-in-a-data-frame

```{r}
connection_events<-connection_events[,c(1:42,44:46, 43)]
connection_events
saveRDS(connection_events, file='./data/adding-kmeans-features.rds')

```

```{r}
for(i in 1:5){
  variablename = paste("kmeans", i, sep = "_")
  columnname = paste("is_kmeans", i, sep = "_")
  assign(variablename, connection_events[connection_events$columnname==1])
}

kmeans_1 <- connection_events[connection_events$is_kmeans_1==1]
kmeans_2 <- connection_events[connection_events$is_kmeans_2==1]
kmeans_2[kmeans_2$label!="smurf."]
kmeans_3 <- connection_events[connection_events$is_kmeans_3==1]
kmeans_4 <- connection_events[connection_events$is_kmeans_4==1]
kmeans_5 <- connection_events[connection_events$is_kmeans_5==1]
kmeans_5

```

```{r}
connection_events <- connection_events[,c('duration','src_bytes','dst_bytes','num_compromised','num_root','count','srv_count','dst_host_count','dst_host_srv_count','label')]
set.seed(20)
kCluster <- kmeans(connection_events[,1:8], 10, nstart = 1)
kCluster$`cluster`
for (i in 1:10){
  connection_events$is_kmeans_1 <- as.integer(kCluster$`cluster`==1)
  connection_events$is_kmeans_2 <- as.integer(kCluster$`cluster`==2)
  connection_events$is_kmeans_3 <- as.integer(kCluster$`cluster`==3)
  connection_events$is_kmeans_4 <- as.integer(kCluster$`cluster`==4)
  kmeans_1 <- connection_events[connection_events$is_kmeans_1==1]
  kmeans_2 <- connection_events[connection_events$is_kmeans_2==1]
  kmeans_3 <- connection_events[connection_events$is_kmeans_3==1]
  kmeans_4 <- connection_events[connection_events$is_kmeans_4==1]
}


```

```{r}
install.packages('BiocManager')
install.packages("ncdf")
library(ncdf)
total <- 0
for (i in 1:50) {
  assign(paste("data", i, sep = ""), get.var.ncdf(nc, varid = nc$var[[i]]))
  total <- total + get(paste("data", i, sep = ""))
}

```

